---
title: "Ch4 Excercises"
output: html_notebook
---

```{r}
library(ISLR2)
library(corrplot)
library(MASS)
library(class)
pairs(Weekly)
```
```{r}
plot(Year~Volume, data = Weekly)
```

```{r}
corrplot(cor(Weekly[,-9]))
```
Year and Volume variables seem to be linearly related. 

```{r}
glm.fit <- glm(Direction ~ Lag1 + Lag2 + Lag3 + Lag4 + Lag5, family = "binomial", data = Weekly)
summary(glm.fit)
```
Lag2 is statistically significant at $\alpha = 0.05

```{r}
probs <- predict(glm.fit, type = "response")
pred <- rep("Down", length(probs))
pred[probs > 0.5] <- "Up"
table(pred, Weekly$Direction)
mean(pred == Weekly$Direction)
```
The model predicted the correct directions of the stock market 56.29% of the time. The model predicted 93.22% of the Up values correctly. It predicted only 10.12% of the Down values correctly
```{r}
attach(Weekly)
train <- Weekly[Year < 2009,]
test <- Weekly[Year > 2008,]
glm.fit <- glm(Direction ~ Lag2, data = train, family = "binomial")
probs <- predict(glm.fit, type = "response", newdata = test)
pred <- rep("Down", length(probs))
pred[probs > 0.5] <- "Up"
table(pred, test$Direction)
mean(pred !=test$Direction)
```
The model predicted the correct directions 62.5% on the test set. 

```{r}
lda.fit <- lda(Direction ~ Lag2, data = train)
pred <- predict(lda.fit, newdata = test, type = "response")
table(pred$class, test$Direction)
mean(pred$class != test$Direction)
```
The LDA model has the same test error rate as the logistic regression model at 37.5%. 

```{r}
qda.fit <- qda(Direction ~ Lag2, data = train)
pred <- predict(qda.fit, newdata = test, type = "response")
table(pred$class, test$Direction)
mean(pred$class != test$Direction)
```
The QDA model performs poorer than LDA with a test error rate of 41.35%. 


